---
title: "R Notebook"
output: html_document
---

```{r}
train = read.csv("train.csv")
test = read.csv("test.csv")
full = rbind(train[,-81], test)
colnames(full)[colSums(is.na(full)) > 0]
colSums(sapply(full, is.na))
```

#MSZoning 
```{r}
MSZoning1 = as.character(full$MSZoning)
MSZoning1[which(is.na(full$MSZoning))] = "Unknown"
full$MSZoning = as.factor(MSZoning1)
```

#LotFrontage 
```{r}
library(mice)
set.seed(1) 
mice.model = mice(full[,c("LotShape","LotArea","LotConfig", "MSSubClass")], method="rf")
mice.output = complete(mice.model)
full$LotFrontage = mice.output$LotFrontage
```

#Alley
```{r}
Alley1 = as.character(full$Alley)
Alley1[which(is.na(full$Alley))] = "None"
full$Alley = as.factor(Alley1)
```

#Utilities
```{r}
Utilities1 = as.character(full$Utilities)
Utilities1[which(is.na(full$Utilities))] = "Unknown"
full$Utilities = as.factor(Utilities1)
```

#Exterior1st, Exterior2nd 
```{r}
index1 = which(is.na(full$Exterior1st))
index2 = which(is.na(full$Exterior2nd))
Exterior1st1 = as.character(full$Exterior1st)
Exterior2nd1 = as.character(full$Exterior2nd)
Exterior1st1[index1] = "Other"
Exterior2nd1[index2] = "Other"
full$Exterior1st = as.factor(Exterior1st1)
full$Exterior2nd = as.factor(Exterior2nd1)
```

#MasVnrType
```{r}
MasVnrType1 = as.character(full$MasVnrType)
MasVnrType1[which(is.na(full$MasVnrType))] = "None"
full$MasVnrType = as.factor(MasVnrType1)
```

#MasVnrArea
```{r}
full$MasVnrArea[which(is.na(full$MasVnrArea) & full$MasVnrType=="None")] = 0
```

#BsmtQual
```{r}
BsmtQual1 = as.character(full$BsmtQual)
BsmtQual1[which(is.na(full$BsmtQual))] = "None"
full$BsmtQual = as.factor(BsmtQual1)
```

#BsmtCond
```{r}
BsmtCond1 = as.character(full$BsmtCond)
BsmtCond1[which(is.na(full$BsmtCond))] = "None"
full$BsmtCond = as.factor(BsmtCond1)
```

#BsmtExposure
```{r}
BsmtExposure1 = as.character(full$BsmtExposure)
BsmtExposure1[which(is.na(full$BsmtExposure))] = "None"
full$BsmtExposure = as.factor(BsmtExposure1)
```

#BsmtFinType1
```{r}
BsmtFinType11 = as.character(full$BsmtFinType1)
BsmtFinType11[which(is.na(full$BsmtFinType1))] = "None"
full$BsmtFinType1 = as.factor(BsmtFinType11)
```

#BsmtFinType2
```{r}
BsmtFinType21 = as.character(full$BsmtFinType2)
BsmtFinType21[which(is.na(full$BsmtFinType2))] = "None"
full$BsmtFinType2 = as.factor(BsmtFinType21)
```

#BsmtFinSF1, BsmtFinSF2, BsmtUnfSF, TotalBsmtSF, BsmtFullBath, BsmtHalfBath
```{r}
index1 = which(is.na(full$BsmtFinSF1))
index2 = which(is.na(full$BsmtFinSF2))
index3 = which(is.na(full$BsmtUnfSF))
index4 = which(is.na(full$TotalBsmtSF))
index5 = which(is.na(full$BsmtFullBath))
index6 = which(is.na(full$BsmtHalfBath))
full$BsmtFinSF1[index1] = 0
full$BsmtFinSF2[index2] = 0
full$BsmtUnfSF[index3] = 0
full$TotalBsmtSF[index4] = 0
full$BsmtFullBath[index5] = 0
full$BsmtHalfBath[index6] = 0
```

#Electrical 
```{r}
Electrical1 = as.character(full$Electrical)
Electrical1[which(is.na(full$Electrical))] = "Unknown"
full$Electrical = as.factor(Electrical1)
```

#KitchenQual
```{r}
index1 = which(is.na(full$KitchenQual))
table(full$KitchenQual)
full$KitchenQual[index1] = "TA"
```

#Functional 
```{r}
Functional1 = as.character(full$Functional)
Functional1[which(is.na(full$Functional))] = "Unknown"
full$Functional = as.factor(Functional1)
```

#FireplaceQu
```{r}
FireplaceQu1 = as.character(full$FireplaceQu)
FireplaceQu1[which(is.na(full$FireplaceQu))] = "None"
full$FireplaceQu = as.factor(FireplaceQu1)
```

#GarageType
```{r}
GarageType1 = as.character(full$GarageType)
GarageType1[which(is.na(full$GarageType))] = "None"
full$GarageType = as.factor(GarageType1)
```

#GarageYrBlt
```{r}
full$GarageYrBlt[which(is.na(full$GarageYrBlt)&full$GarageType=="None")] = 0 
index = which(is.na(full$GarageYrBlt)&full$GarageType!="None")
mice.model = mice(full[,c("GarageType", "GarageYrBlt", "GarageFinish", "GarageCars", "GarageArea", "GarageQual", "GarageCond", "YearBuilt", "YearRemodAdd", "OverallQual")], method="rf")
mice.output = complete(mice.model)
full[index, ]$GarageYrBlt = mice.output[index, ]$GarageYrBlt
```

#GarageFinish
```{r}
GarageFinish1 = as.character(full$GarageFinish)
GarageFinish1[which(is.na(full$GarageFinish)&full$GarageType=="None")] = "None"
full$GarageFinish = as.factor(GarageFinish1)
index = which(is.na(full$GarageFinish)&full$GarageType!="None")
full[index, ]$GarageFinish = mice.output[index, ]$GarageFinish
```

#GarageCars, GarageArea
```{r}
index1 = which(is.na(full$GarageCars&full$GarageType!="None"))
index2 = which(is.na(full$GarageArea&full$GarageType!="None"))
full[index1, ]$GarageCars = mice.output[index1, ]$GarageCars
full[index2, ]$GarageArea = mice.output[index2, ]$GarageArea
```

#GarageQual
```{r}
GarageQual1 = as.character(full$GarageQual)
GarageQual1[which(is.na(full$GarageQual)&full$GarageType=="None")] = "None"
full$GarageQual = as.factor(GarageQual1)
index = which(is.na(full$GarageQual)&full$GarageType!="None")
full[index, ]$GarageQual = mice.output[index, ]$GarageQual
```

#GarageCond
```{r}
GarageCond1 = as.character(full$GarageCond)
GarageCond1[which(is.na(full$GarageCond)&full$GarageType=="None")] = "None"
full$GarageCond = as.factor(GarageCond1)
index = which(is.na(full$GarageCond)&full$GarageType!="None")
full[index, ]$GarageCond = mice.output[index, ]$GarageCond
```

#PoolQC
```{r}
PoolQC1 = as.character(full$PoolQC)
PoolQC1[which(is.na(full$PoolQC))] = "None"
full$PoolQC = as.factor(PoolQC1)
```

#Fence
```{r}
Fence1 = as.character(full$Fence)
Fence1[which(is.na(full$Fence))] = "None"
full$Fence = as.factor(Fence1)
```

#MiscFeature
```{r}
MiscFeature1 = as.character(full$MiscFeature)
MiscFeature1[which(is.na(full$MiscFeature))] = "None"
full$MiscFeature = as.factor(MiscFeature1)
```

#SaleType
```{r}
index = which(is.na(full$SaleType))
full$SaleType[index] = "Oth"
```

```{r}
colSums(sapply(full, is.na))
write.csv(full,file="full.csv",row.names=F)
```